---
title: "WAST"
author: "Bethan"
date: "11/11/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "Networked Data Lab: Mental health crises in children and teenagers"
author: "Public Health Wales"
date: "`r Sys.Date()`"
output:
prettydoc::html_pretty:
highlight: github
---



```{r setup, include=FALSE}
#Load packages
library("tidyverse")
library("plotly")
library("rmarkdown")
library("knitr")
library("scales")
library("viridis")



#Load WAST data
WAST_data <- read.csv(file = 'WAST-data.csv')



#Add a new column
WAST_data <- WAST_data %>%
mutate(labels = scales::percent(pct))
```



## Data sources



These are the following data sources used for this project.



- PEDW
- WAST
- ED
- And others



## Share of ambulance calls related to mental health



```{r WAST.preview, echo=FALSE, message=FALSE, warning=FALSE}



#Display underlying data in a table
WAST_data %>%
kable(.,digits=1,format.args = list(big.mark = ",")) %>%
kableExtra::kable_styling(.,bootstrap_options = c("striped", "hover"),full_width = F, font_size= 12)



#Display a pie chart
pie_chart <- ggplot(WAST_data, aes(x = "", y = pct, fill = cause)) +
facet_wrap(~year) +
geom_col(color = "black") +
geom_label(aes(label = labels), color = c("white"),
position = position_stack(vjust = 0.5),
show.legend = FALSE) +
guides(fill = guide_legend(title = "Attendance")) +
coord_polar(theta = "y") +
theme_void()



pie_chart
```



## About the Networked Data Lab



The [Networked Data Lab](https://www.health.org.uk/funding-and-partnerships/our-partnerships/the-networked-data-lab) is a Health Foundation funded collaboration between five analytical partners in the UK.
